Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-12 paper.tex

\section{\uppercase{Discussion}}
\label{sec:discussion}
There are a few places where \mEdhoc{} can be improved,
which we found during this work and communicated to the authors.
%
We discuss them below.
%

>>>>

%-------------------------------------------------------------------------- sec
\section{\uppercase{Error handling}}
\label{sec:errorHandling}
\mPoint{Error handling is undefined except for algo negotiation}
Section 6 of the \mEdhoc{} specification\footnote{draft-ietf-lake-edhoc-14}
states that error messages can be sent at any time and by any party.
%
One error message type is defined (for algorithm negotiation), and the rest can
be arbitrarily defined by the implementation.
%
The contents and semantics of these messages are also implementation defined.
%
Consequently, the error messages provide a generic message passing mechanism.
%

\textbf{Q:} Is htere any situation where it makes sense that the initiator sends
a unsupported ciphersuite message instead of message 3?
%

\textbf{Q:} In Section H: if no message correlation support by the transport
layer, \mCi{} and \mCr{} should be used for correlation of messages to a
session.
%
Error messages do not carry \mCi{} or \mCr{}; will this create a problem?
%

\mEdhoc{} provides the error message mechanism, but gives little to no guidance
on how it should be used safely.
%
Example of issue with improper use: Assume application logs error messages a
finite log with log rotation.
%
If the log is used for anomaly detection or detection of sensitive events, then
an adversary can simply inject error messages and fill the log until the
sensitive event is overwritten.
%
If the filling error messages are less suspicious than the actual attack, this
may be beneficial for the adversary.
%
Implementors should do proper log-separation and log management.
%

Section 6.2 gives an excample of sending an error message "method not
supported".
%
This message cannot be used to negotiate method securely.
%
The reason is that error messages are not integrity protected, and an initator
only proposes one method, and therefore the same tactic used for ciphersuite
negotiation cannot be used for methods.
%
Because method negotiation can be viewed in the context of crypto agility, there
is room for improvement.
%

%-------------------------------------------------------------------------- sub
\section{\uppercase{Discussion}}
\label{sec:discussion}
There are a few places where \mEdhoc{} can be improved,
which we found during this work and communicated to the authors.
%
We discuss them below.
%
